Deep Probabilistic Models for Camera Geo-Calibration

### 2018-10-24 chapters/crosstransf/paper.tex
minor change
geolocalization -> geo-localization geocalibration -> geo-calibration

Learning-based methods for pixel-level labeling of aerial imagery
have long relied on manually annotated training data. Unfortunately,
such data is expensive to create. Furthermore, its value is limited
because a method trained on one dataset will typically not perform
well when applied to another source of aerial imagery.  The
difficulty in obtaining datasets of sufficient scale for all
modalities has hampered progress in applying deep learning techniques
to aerial imagery.  There have been a few notable
exceptions~\cite{mnih2010learning,paisitkriangkrai2015effective}, but
these have all used fairly coarse grained semantic classes, covered a
small spatial area, and are limited to modalities in which human
annotators are able to manually assign labels.

@@

There has been significant interest recently in predicting
ground image features from aerial imagery for the task of
ground image geolocalization~\cite{workman2015wide}. Our work is
unique in that it is the first to attempt to predict a dense
pixel-level segmentation of the ground image. We demonstrate the
value of this approach in several ways.

@@

\paragraph{Relating Aerial and Ground-Level Viewpoints}
Several methods have been recently proposed to jointly reason about
co-located aerial and ground image pairs. Luo
\etal~\cite{luo2008event} demonstrate that aerial imagery can aid
in recognizing the visual content of a geo-tagged ground image.
M{\'a}ttyus \etal~\cite{mattyus2016hd} perform joint inference over
monocular aerial imagery and stereo ground images for fine-grained
road segmentation. Wegner \etal~\cite{wegner2016cataloging} build a
map of street trees. Given the horizon line and the camera intrinsics,
Ghouaiel and Lef{\`e}vre~\cite{ghouaiel2016coupling} transform
geo-tagged ground-level panoramas to a top-down view to enable
comparisons with aerial imagery for the task of change detection.
Recent work on cross-view image
geolocalization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
 has shown that convolutional neural
networks are capable of extracting features from aerial imagery
that can be matched to features extracted from ground imagery.
Vo \etal~\cite{vo2016localizing} extend this line of work,
demonstrating improved geolocalization performance by applying an
auxiliary loss function to regress the ground-level camera orientation
with respect to the aerial image. To our knowledge, our work is the
first work to explore predicting the semantic layout of a ground
image from an aerial image.

@@

\section{Evaluation and Applications}
In this section, we will show that our network architecture can be
used in four different tasks: 1) weakly supervised semantic learning, 
2) aerial imagery labeling, 3) orientation regression and geocalibration, 
and 4) cross-view image synthesis. Additional qualitative results and 
the complete network structure used for cross-view image synthesis 
can be found in our supplemental materials.

@@

\subsection{Cross-view for Geocalibration}

@@

\item{\textbf{CVUSA:}} We use the test set introduced
in~\secref{dataset_cross} to create this dataset, it has two parts for
orientation estimation and geocalibration, respectively.  For the
orientation regression task, we rotate the aerial image to a random
angle. For the fine-grained geocalibration experiment, we center-crop
the aerial image around a random $x,y$ offset, then rotate the image to a
random angle.  In both experiments, the heading direction of the
ground images are the same. We center crop a 224 $\times$ 448
cutout from each ground image as the query image.

@@

\paragraph{Fine-grained Geocalibration}

@@

  \caption{Fine-grained geocalibration results on CVUSA. (left) From
top to bottom are the $I_g$, $L_g$, and $L_{g'}$ respectively.  We
visualize three classes on the labels: {\em road} (red), {\em
vegetation} (green), and {\em man-made} (blue).  (right) Orientation
flow map (red), where the arrow direction indicates the optimal
direction at that location and length indicates the magnitude. We also
show the optimal prediction and the ground-truth frustums in blue and
green respectively.}
  \label{fig:geocali:cali}
\end{figure*}

>>>>

In this chapter, we will exploit overhead imagery to construct
the constraint function for the camera orientation and location.
%
Learning-based methods for pixel-level labeling of aerial imagery
have long relied on manually annotated training data. Unfortunately,
such data is expensive to create. Furthermore, its value is limited
because a method trained on one dataset will typically not perform
well when applied to another source of aerial imagery.  The
difficulty in obtaining datasets of sufficient scale for all
modalities has hampered progress in applying deep learning techniques
to aerial imagery.  There have been a few notable
exceptions~\cite{mnih2010learning,paisitkriangkrai2015effective}, but
these have all used fairly coarse grained semantic classes, covered a
small spatial area, and are limited to modalities in which human
annotators are able to manually assign labels.

@@

There has been significant interest recently in predicting
ground image features from aerial imagery for the task of
ground image geo-localization~\cite{workman2015wide}. Our work is
unique in that it is the first to attempt to predict a dense
pixel-level segmentation of the ground image. We demonstrate the
value of this approach in several ways.

@@

\paragraph{Relating Aerial and Ground-Level Viewpoints}
Several methods have been recently proposed to jointly reason about
co-located aerial and ground image pairs. Luo
\etal~\cite{luo2008event} demonstrate that aerial imagery can aid
in recognizing the visual content of a geo-tagged ground image.
M{\'a}ttyus \etal~\cite{mattyus2016hd} perform joint inference over
monocular aerial imagery and stereo ground images for fine-grained
road segmentation. Wegner \etal~\cite{wegner2016cataloging} build a
map of street trees. Given the horizon line and the camera intrinsics,
Ghouaiel and Lef{\`e}vre~\cite{ghouaiel2016coupling} transform
geo-tagged ground-level panoramas to a top-down view to enable
comparisons with aerial imagery for the task of change detection.
Recent work on cross-view image
geo-localization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
 has shown that convolutional neural
networks are capable of extracting features from aerial imagery
that can be matched to features extracted from ground imagery.
Vo \etal~\cite{vo2016localizing} extend this line of work,
demonstrating improved geo-localization performance by applying an
auxiliary loss function to regress the ground-level camera orientation
with respect to the aerial image. To our knowledge, our work is the
first work to explore predicting the semantic layout of a ground
image from an aerial image.

@@

\section{Evaluation and Applications}
In this section, we will show that our network architecture can be
used in four different tasks: 1) weakly supervised semantic learning, 
2) aerial imagery labeling, 3) orientation regression and geo-calibration, 
and 4) cross-view image synthesis. Additional qualitative results and 
the complete network structure used for cross-view image synthesis 
can be found in our supplemental materials.

@@

\subsection{Cross-view for Geo-Calibration}

@@

\item{\textbf{CVUSA:}} We use the test set introduced
in~\secref{dataset_cross} to create this dataset, it has two parts for
orientation estimation and geo-calibration, respectively.  For the
orientation regression task, we rotate the aerial image to a random
angle. For the fine-grained geo-calibration experiment, we center-crop
the aerial image around a random $x,y$ offset, then rotate the image to a
random angle.  In both experiments, the heading direction of the
ground images are the same. We center crop a 224 $\times$ 448
cutout from each ground image as the query image.

@@

\paragraph{Fine-grained Geo-Calibration}

@@

  \caption{Fine-grained geo-calibration results on CVUSA. (left) From
top to bottom are the $I_g$, $L_g$, and $L_{g'}$ respectively.  We
visualize three classes on the labels: {\em road} (red), {\em
vegetation} (green), and {\em man-made} (blue).  (right) Orientation
flow map (red), where the arrow direction indicates the optimal
direction at that location and length indicates the magnitude. We also
show the optimal prediction and the ground-truth frustums in blue and
green respectively.}
  \label{fig:geocali:cali}
\end{figure*}

### 2018-10-24 chapters/fasthorizon/paper.tex
fix duplicate label definition
constraint functions
geolocalization -> geo-localization geocalibration -> geo-calibration

Automatic vanishing point (VP) and horizon line detection are two of
the most fundamental problems in geometric computer
vision~\cite{barnard1983interpreting,magee1984determining}. Knowledge
of these quantities is the foundation for many higher level
tasks, including image mensuration~\cite{criminisi2000single},
facade detection~\cite{liulocal2014},
geolocalization~\cite{baatz2010handling,workman2014rainbow}, and
camera
calibration~\cite{autorecovery2000,grammatikopoulos2007automatic,
jacobs13cloudcalibration,videocampass2002}. Recent work in this area
\cite{global2013,wildenauer2012,kitware2013} has explored novel
problem formulations that significantly increase robustness to noise.

@@

%
% Evaluation
%
\section{Evaluation}
\label{sec:evaluation}

@@

\begin{figure*}[]
  \centering
  \begin{subfigure}{.30\linewidth}
    \centering
    \includegraphics[width=\linewidth]{fasthorizon/YUD_methods}
    \subcaption{YUD}
    \label{fig:horError_YUD}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.3\linewidth}
    \centering
    \includegraphics[width=\linewidth]{fasthorizon/ECD_methods}
    \subcaption{ECD}
    \label{fig:horError_ECD}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.3\linewidth}
    \centering
    \includegraphics[width=\linewidth]{fasthorizon/HLW_methods}
    \subcaption{HLW}
    \label{fig:hlw_err}
  \end{subfigure}
  \caption{For three benchmark datasets, the fraction of images
    (y-axis) with a horizon error less than a threshold (x-axis). The
    AUC for each curve is shown in the legend. For additional details see \secref{evaluation}.}
  \label{fig:horError}
\end{figure*}

>>>>

In this chapter, we will develop a constraint function for
camera pose. Since the camera roll and pitch angle can be derived from
the horizon line position, our algorithm focuses on detecting the
horizon line from the input image.

Automatic vanishing point (VP) and horizon line detection are two of
the most fundamental problems in geometric computer
vision~\cite{barnard1983interpreting,magee1984determining}. Knowledge
of these quantities is the foundation for many higher level
tasks, including image mensuration~\cite{criminisi2000single},
facade detection~\cite{liulocal2014},
geo-localization~\cite{baatz2010handling,workman2014rainbow}, and
camera
calibration~\cite{autorecovery2000,grammatikopoulos2007automatic,
jacobs13cloudcalibration,videocampass2002}. Recent work in this area
\cite{global2013,wildenauer2012,kitware2013} has explored novel
problem formulations that significantly increase robustness to noise.

@@

%
% Evaluation
%
\section{Evaluation}
\label{sec:evaluation_fast}

@@

\begin{figure*}[]
  \centering
  \begin{subfigure}{.30\linewidth}
    \centering
    \includegraphics[width=\linewidth]{fasthorizon/YUD_methods}
    \subcaption{YUD}
    \label{fig:horError_YUD}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.3\linewidth}
    \centering
    \includegraphics[width=\linewidth]{fasthorizon/ECD_methods}
    \subcaption{ECD}
    \label{fig:horError_ECD}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.3\linewidth}
    \centering
    \includegraphics[width=\linewidth]{fasthorizon/HLW_methods}
    \subcaption{HLW}
    \label{fig:hlw_err}
  \end{subfigure}
  \caption{For three benchmark datasets, the fraction of images
    (y-axis) with a horizon error less than a threshold (x-axis). The
    AUC for each curve is shown in the legend. For additional details
see \secref{evaluation_fast}.}
  \label{fig:horError}
\end{figure*}
